---
title: "chapter4DV"
format: html
embedded resources: true 
editor: visual
---

## Question 1 

```{r}
library(tidyverse)
```

```{r}
tv_ratings <- read_csv("https://raw.githubusercontent.com/vaiseys/dav-course/main/Data/tv_ratings.csv")
```

```{r}
glimpse(tv_ratings)
```

```{r}
tv_long <- tv_ratings %>% 
  group_by(title) %>% 
  summarise(num_seasons = n()) %>% 
  ungroup() %>% 
  left_join(tv_ratings, by = "title") 

tv_long <- tv_long %>% 
  filter(num_seasons >= 5)
```

```{r}
ggplot(tv_long,
       mapping = aes(x = av_rating,
                     y = seasonNumber,
                     group = title)) +
  geom_line() 
```

There are not really any conclusions to be drawn from this line plot, however there is a lot of data in between 7 to 9 in average rating.

## Question 2 

```{r}
tv_long <- tv_ratings |>
  group_by(title) |>
  mutate(nseasons = max(seasonNumber)) |>
filter(nseasons >= 5) |>
  ungroup()

ggplot(tv_long,
       mapping = aes(x = av_rating,
                     y = seasonNumber,
                     group = title)) +
  geom_line(alpha = .2) +
  facet_wrap(~genres) +
  theme_minimal()
```

The show that tends to last longer is action, crime, and drama.

Ratings change as the show starts to get into later seasons. At first they are pretty stable but than as it gets to later seasons its starts to change a lot.

The show on Drama, Family, Fantasy whose rating just plummeted is "Are You Afraid of the Dark"

## Question 3 

```{r}
tv_ratings |>
  filter(av_rating >= 9) 
```

```{r}
tv_ratings |>
  filter(av_rating >= 9) |>
ggplot(tv_ratings,
       mapping = aes(x = genres)) +
  geom_bar() +
  coord_flip()
```

The genre with the most top-rated show is Drama.

## Question 4 

```{r}
comedies_dramas <- tv_ratings %>% 
  mutate(is_comedy = if_else(str_detect(genres, "Comedy"), 
                             1, 
                             0)) %>% # If it contains the word comedy then 1, else 0
  filter(is_comedy == 1 | genres == "Drama") %>% # Keep comedies and dramas
  mutate(genres = if_else(genres == "Drama", # Make it so that we only have those two genres
                          "Drama", 
                          "Comedy"))

glimpse(comedies_dramas)
```

```{r}
comedies_dramas |>
ggplot(tv_ratings,
       mapping = aes(x = av_rating,
                     fill = genres)) +
  geom_density(alpha=.5)
  
```

Your prediction that comedies should rival the best dramas is true. In fact there are higher rated comedies than dramas.

## Question 5 

```{r}
comedies_dramas |>
ggplot(tv_ratings,
       mapping = aes(x = av_rating,
                     fill = genres)) +
  geom_histogram(alpha=.5)
```

The histogram gives us more direct information about how highly these genres are ranked. It shows that the comedies are actually a lot more highly rated.

```{r}
comedies_dramas |>
ggplot(tv_ratings,
       mapping = aes(x = av_rating,
                     fill = genres)) +
  geom_freqpoly()
```

I notice that it looks very similar to the histogram however it is just a line instead of direct numbers. I think of the three plots the second one was the most informative. The histogram gave exact numbers and showed how big of a difference in ratings there was between comedy and drama.

## Question 6 

```{r}
comedies_dramas |>
ggplot(tv_ratings,
       mapping = aes(x = av_rating,
                     y = share)) +
  geom_bin_2d()
```

```{r}
comedies_dramas |>
ggplot(tv_ratings,
       mapping = aes(x = av_rating,
                     y = share)) +
  geom_point()

```

I see that the majority of of average ratings occur between 7 and 9. In comparison to a scatter plot this shows it shows similar information. It shows where the points are clustered however the bin 2d gives a lot better way to show where the points are directly clustered in relation to the average ratings.

```{r}
comedies_dramas |>
ggplot(tv_ratings,
       mapping = aes(x = av_rating,
                     y = share,
                     fill = genres)) +
  geom_bin_2d()
```

When we add genres to the fill aesthetic the pattern I see is that drama has a lot less shares compared to comedy that has higher shares for the most part. There was one big outlier in drama and that was Dekalog.
