---
title: "md07"
format: html
embed-resources: true
editor: visual
---

## 

```{r}
library(tidyverse)
library(here)
library(moderndive)
theme_set(theme_minimal())

nobel_winners <- read_csv("https://raw.githubusercontent.com/vaiseys/dav-course/main/Data/nobel_winners.csv")
```

```{r}
nobel_winners_flt <- nobel_winners %>% 
  filter(category != "Peace") %>% 
  mutate(is_us = if_else(birth_country == "United States of America", 1, 0))

true_prop <- nobel_winners_flt %>% 
  group_by(is_us) %>% 
  summarise(prop = n()/nrow(nobel_winners_flt))

ggplot() + 
  coord_cartesian(xlim = c(0,1), ylim = c(0,1)) + 
  geom_vline(xintercept = true_prop[2,2][[1]], linetype = "dashed")  + 
  labs(x = "Proportion")
```

The *true* proportion of US-born Nobel prize winners is 0.306317.

```{r}
set.seed(33)
# Random sample 
our_sample <- sample_n(nobel_winners_flt, 
                       size = 25, 
                       replace = F)

sample_prop <- our_sample %>% 
  group_by(is_us) %>% 
  summarise(prop = n()/nrow(our_sample))


ggplot() + 
  coord_cartesian(xlim = c(0,1), ylim = c(0,1)) + 
  geom_vline(xintercept = true_prop[2,2][[1]], linetype = "dashed")  + 
  geom_vline(xintercept = sample_prop[2,2][[1]], linetype = "dotted", col = "red") +
  labs(x = "Proportion")
```

The proportion is very far off. It is too high since the line is just about 50.

## Question 1

#  

The population is the whole list of Nobel winners.

The sample frame is "nobel_winners_flt"

The black line is representing the population of the Nobel winners who were US-born.

The red line is representing the sample proportion of the data.

## Question 2 

```{r}
set.seed(33)
repeated_sample <- rep_sample_n(nobel_winners_flt,
                                size = 25,
                                reps = 50)
```

```{r}
sample_proportions <- repeated_sample %>%
  group_by(replicate) %>%
  summarize(proportion = mean(is_us))

mean_sample_proportion <- mean(sample_proportions$proportion)

ggplot(sample_proportions, aes(x=proportion)) + 
  coord_cartesian(xlim = c(0,1)) + 
  geom_histogram(binwidth = 0.05, boundary = 0.4, color = "white") +
  geom_vline(xintercept = mean(nobel_winners_flt$is_us), linetype = "dashed")  + 
  geom_vline(xintercept = mean_sample_proportion, linetype = "dotted", col = "red") +
  labs(x = "Proportion of 25-winner samples that were US-born")
```

## Question 3 

```{r}
repeated_sample_100 <- rep_sample_n(nobel_winners_flt,
                                size = 100,
                                reps = 50)
```

```{r}
sample_proportions_100 <- repeated_sample_100 %>%
  group_by(replicate) %>%
  summarize(proportion = mean(is_us))

mean_sample_proportion_100 <- mean(sample_proportions_100$proportion)

ggplot(sample_proportions_100, aes(x=proportion)) + 
  coord_cartesian(xlim = c(0,1)) + 
  geom_histogram(binwidth = 0.05, boundary = 0.4, color = "white") +
  geom_vline(xintercept = mean(nobel_winners_flt$is_us), linetype = "dashed")  + 
  geom_vline(xintercept = mean_sample_proportion_100, linetype = "dotted", col = "red") +
  labs(x = "Proportion of 100-winner samples that were US-born")
```

The distribution of the 25 winner sample is a lot more fluid than the 100 winner sample. If the data set were smaller it would allow for different results instead of big repeated results.

## Question 4 

```{r}
std_dev_sample_25 <- sd(sample_proportions$proportion)

std_dev_sample_100 <- sd(sample_proportions_100$proportion)


std_dev_sample_25
std_dev_sample_100
```

The sd for the 100 winner sample is smaller than the 25 winner. By more than double is it smaller which means that the results are a lot closer to the median.

```{r}
nobel_winners_w <- nobel_winners %>%
  filter(!is.na(gender))

women_true_prop <- nobel_winners_w %>%
  group_by(gender) %>% 
  summarise(prop = n()/nrow(nobel_winners_w))
```

The true proportion of women winners is 0.05302227

```{r}
nobel_winners_w <- nobel_winners_w %>% 
  mutate(is_w = if_else(gender == "Female", 1, 0))
```

```{r}
ggplot() + 
  coord_cartesian(xlim = c(0,1), ylim = c(0,1)) + 
  geom_vline(xintercept = mean(nobel_winners_w$is_w), linetype = "dashed")  + 
  labs(x = "Proportion")
```

```{r}
set.seed(33)
repeated_sample_w <- rep_sample_n(nobel_winners_w,
                                size = 100,
                                reps = 50)
```

```{r}
sample_proportions_w <- repeated_sample_w %>%
  group_by(replicate) %>%
  summarize(proportion = mean(is_w))

mean_sample_proportion_w <- mean(sample_proportions_w$proportion)
```

```{r}
ggplot(sample_proportions_w, aes(x=proportion)) + 
  coord_cartesian(xlim = c(0,1)) + 
  geom_histogram(binwidth = 0.02, boundary = 0.4, color = "white") +
  geom_vline(xintercept = mean(nobel_winners_w$is_w), linetype = "dashed")  + 
  geom_vline(xintercept = mean(sample_proportions_w$proportion), linetype = "dotted", col = "red") +
  labs(x = "Proportion of 100-winner samples that were woman-identifying")
```

The true value calculated is very accurate and almost exact.

0.0542 is the calculation and the one we made was 0.5302227,

## Question 6 

The central limit thoerem is a statistical concept that says when you have a big enough sample size, the distributions of the populations sample will be almost distributed normally.
