---
title: "MD6EXTRA"
format: html
embed-resources: true
editor: visual
---

```{r}
#| message: false
library(tidyverse)
library(moderndive)
theme_set(theme_minimal())
```

```{r}
data(bikes, package = "bayesrules")
glimpse(bikes)
```

```{r}
data(bikes, package = "bayesrules")
glimpse(bikes)
```

## Question 0

There are 500 rows in the data set.

Each row represents the data for one day.

The dates that the dataset covers are January 2011 to December 2012. However, in July the data only covers one day of that month.

The highest observed ridership in the dataset was 6946.

The highest wind speed recorded in the dataset was 34 mph.

## Question 1

```{r}
get_correlation(rides ~ temp_feel,
                data = bikes) %>% round(2)
```

The correlation between number of rides and what the temperature feels like .58.

```{r}
get_correlation(rides ~ temp_feel,
                data = bikes) %>% round(2)
```

The correlation between the number of rides and wind speed is -.19.

## Question 2

### {r}

```{r}
bikes <- bikes |>
  mutate(wind_kph = windspeed * 1.61)
```

```{r}
get_correlation(windspeed ~ wind_kph,
                data = bikes)
```

```{The correlation between the wind speed in MPH and the wind speed in KPH is 1. The reason that it is 1 is because every kph point is 1.6 times the MPH. This means that this unit conversion will have a slope of 0 making the correlation exactly 1.}

## Question 3 

mph_model <- lm(rides ~ windspeed,
                data = bikes)
get_regression_table(mph_model) %>% 
  select(term, estimate)
```

```{r}
kph_model <- lm(rides ~ wind_kph,
                data = bikes)
get_regression_table(kph_model) %>% 
  select(term, estimate)
```

For both of the sets, the intercepts are 4205.065. The intercepts are the same because it just means that the variable that is predicting rides is equal to what the predictions are. 0mph=0kph.

## Question 4

The predicted ridership for a day with 20KPH would be 3094.605

rides = 4205.065 - 55.523(20KPH) = 3094.605

The predicted ridership for a day with 20MPH would be 3515.345

rides = 4205.065 - 34.486 (20MPH) = 3,515.345

## Question 5

```{r}
bikes <- bikes %>% 
  mutate(temp_c = (temp_feel-32)*(5/9))
```

```{r}
mult_model <- lm(rides ~ wind_kph + temp_c,
                 data = bikes)
get_regression_table(mult_model) %>% 
  select(term, estimate)
```

For a 1 degree celsius increase temperature, the model expects an increase of 143 in ridership.

For every 1kph increase in wind speed, the model expects a decrease of 20 in ridership.

The intercept means that on a day when the temperature is 0 degrees celsius the temperature would be 942.

## Question 6

```{r}
pred_df <- tibble(
  situation = 1:3,
  temp_c = c(25, 15, 10),
  wind_kph = c(15, 5, 40)
)

pred_df$predicted_ridership <- predict(mult_model, newdata = pred_df)
print(pred_df)
```

The ridership predictions that I got were 4226 riders and 1581 riders for 1, 2, and 3 situations.

## Question 7

```{r}
bikes <- bikes %>% mutate(weekend = as.factor(weekend))
weekend_model <- lm(rides ~ wind_kph + weekend + temp_c,
                    data = bikes)
get_regression_table(weekend_model) %>%
  select(term, estimate)
```

The weekend coefficient tells us that during a weekend the ridership should be 714 riders less than on a weekday.

## Question 8

```{r}
library(ggeffects)
predictions <- ggpredict(weekend_model,
                         terms = c("weekend"),
                         ci_level = NA) # don't think about confidence intervals yet (soon!)
predictions
```

The expected ridership for a weekend is 2970 riders.

The expected ridership for a weekday is 2683 riders.

## Question 9

```{r}
bikerides <- predict(weekend_model)
residuals <- bikes$rides - bikerides
broom::tidy(residuals)
residuals
```

The model is so wrong about this day because on this day was when a hurricane was striking. Many places closed down and shut down their towns. This would explain the low ridership because there was no one out compared to nearly any other day of the year. This day was October 29, 2012.
